---
title: "hello-foofactorsran"
author: "Ran Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This documents contains detailed information of the functions in the `foofactorsran` package. 

##Define an age group

`age_group()` takes a numeric vector (ages) with each element in the vector bigger than 0 and smaller than 120 to be a valid age. It returns a factor of the same length as the input and replaces each age by its agegroup. The age groups are defined as follows: 

- 0<x<=14: "Children"
- 14<x<=24: "Youth"
- 24<x<=65: "Adult"
- 65<x : "Senior"

If `droplevel = FALSE`, the levels for x will be `c("Children","Youth","Adult","Senior")`. If `droplevel = TRUE`, which is also the default setting, the unused levels of age groups will be droped, but the order of levels stay as the same. 

Example:
```{r,include=FALSE}
library(foofactorsran)

```


```{r}
x <- c(2,45,22,27)
age_group(x)
age_group(x,droplevel = T)
age_group(x,droplevel = FALSE)
```


The following input would produce an error.

```{r,eval=FALSE}
oops1 <- age_group(c(12,56),droplevel = 2)
oops2 <- age_group(c(-1,56))
```


##Reorder factor levels

`factor_level()` is a fucntion that convert the input x to a factor and defines the order of factor levels at the same time. The `level` argument is set to `"alp"` by default which means the levels will be ordered alphabatically. If `level = "asit"`, the  factor levels will be set in the order they appear in x. User can also define the level order as they define in the function `factor()`, other arguments of `factor()` can be passed to `factor_level()` as well.

To avoid turing a value of x to "NA" by defining levels (like `factor()` sometimes does), only level with the same length as original number of levels (or number of levels of as.factor(x) if x is not originally a factor), and the level must inclused all values of x. Note that `factor_level()` would not drop unused levels if the input x is a factor. 

Examples:

```{r}
x <- factor(c("b","b","a","c","d","a"),levels = c("c","a","b","d","e"))

factor_level(x, level = c("e","d","c","b","a"))
factor_level(x)
factor_level(x,"asit")
```


The following will produce an error.

```{r, eval=FALSE}

y <- c("aa","aa","cc","bb","cc")
z <- as.factor(y)
factor_level(y, level = c("aa","cc"))
factor_level(z, level = c("aa","cc"))

factor_level(y, level = c("red","green","blue"))
factor_level(z, level = c("red","green","blue"))
```

Factor_level() can pass arguments of the function `factor()` only if the `level`argument is user defined. To see an example:

```{r}
v <- c("apple","apple","orange","pear")
factor_level(v,level = c("apple","pear","orange"), labels = c("red","orange","yellow"))
```


`order_asit()` is a function that takes a vector of characters (or a factor) and returns a factor with order of levels defined in the way they appear in x. `order_asit(x)` is equitvalent to `factor_level(x,"asit")`. Note that a warning would show up if the input has many unique values (same thing applies to `factor_level()`). 

```{r}
w <- as.factor(c("a","b","d","c","e"))
order_asit(w)
```








Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
